A free/open-source Kazakh-Tatar machine translation system

### 2013-04-06 paper/paper.tex
NO MOAR ERRORS
cleaner

\usepackage{fontspec}
\defaultfontfeatures{PunctuationSpace=3,Scale=MatchLowercase,Mapping=tex-text}
\newfontfeature{IPA}{+mgrk}
%\setromanfont[IPA]{FreeSerif}
\setromanfont[Scale=0.9]{Times New Roman}
\newfontfamily\qipa[IPA,Scale=MatchLowercase]{FreeSerif}

@@

%FIXME
%\name{Jonathan North Washington, Francis M. Tyers and Ilnar Salimzyanov}

%\address{ Indiana University, Universitat d'Alacant, Kazan Federal University \\
%          Bloomington, Alacant, Kazan\\
%          IN 47405 (USA), E-03071 Spain, Russia\\
%          \email{jonwashi@indiana.edu}, \email{ftyers@dlsi.ua.es},  \email{ilnar.salimzyan@gmail.com} \\
%}

@@

%\abstract{
%This paper presents a bidirectional machine translation system between
%Kazakh and Tatar.
% \\
%%FIXME
%%\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
%}

@@

\author{Ilnar Salimzyanov\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  {\tt email@domain}  \And
  Jonathan North Washington\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  {\tt email@domain}  \And
  Francis Morton Tyers\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  {\tt email@domain}}

@@

>>>>

\usepackage{fontspec}
\defaultfontfeatures{PunctuationSpace=3,Scale=MatchLowercase,Mapping=tex-text}
\newfontfeature{IPA}{+mgrk}
%\setromanfont[IPA]{FreeSerif}
\setromanfont[Scale=0.9]{Times New Roman}
\newfontfamily\qipa[IPA,Scale=MatchLowercase]{FreeSerif}
\setmonofont[Scale=0.7]{DejaVu Sans Mono}

@@

@@

%%\Keywords{Kazakh, Tatar, MT, Free software, Open-source}

@@

\author{Ilnar Salimzyanov\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  \email{email@domain}  \And
  Jonathan North Washington\\
  Departments of Linguistics\\
  and Central Eurasian Studies\\
  Indiana University\\
  Bloomington, Indiana\\
  \email{jonwashi@indiana.edu}  \And
  Francis Morton Tyers\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  \email{email@domain}}

@@

%FIXME: Contrastive grammar
